quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-03 paper-quollr.Rmd
Removed unncessary commented chunks

```{r setup, include=FALSE}
options(repos = "https://cloud.r-project.org") ## set up CRAN mirror
knitr::opts_chunk$set(
  echo = FALSE, 
  cache=FALSE, 
  message=FALSE, 
  warning=FALSE,
  comment = ">",
  out.width = "100%")

@@

<!-- # Find the most appropriate fit -->

<!-- ```{r} -->
<!-- #| label: scurve-diff-umap-layouts -->

<!-- nldr_scaled_obj <- gen_scaled_data( -->
<!--   nldr_data = scurve_umap) -->
<!-- umap_scaled1 <- nldr_scaled_obj$scaled_nldr -->

<!-- scurve_nldr1 <- umap_scaled1 |> -->
<!--   ggplot(aes(x = emb1, -->
<!--              y = emb2))+ -->
<!--   geom_point(alpha=0.1, size=1, colour='#e41a1c') + -->
<!--   interior_annotation("a", c(0.08, 0.9)) -->

<!-- nldr_scaled_obj2 <- gen_scaled_data( -->
<!--   nldr_data = scurve_umap2) -->
<!-- umap_scaled2 <- nldr_scaled_obj2$scaled_nldr -->

<!-- scurve_nldr2 <- umap_scaled2 |> -->
<!--   ggplot(aes(x = emb1, -->
<!--              y = emb2))+ -->
<!--   geom_point(alpha=0.1, size=1, colour='#ff7f00') + -->
<!--   interior_annotation("b") -->

<!-- nldr_scaled_obj3 <- gen_scaled_data( -->
<!--   nldr_data = scurve_umap3) -->
<!-- umap_scaled3 <- nldr_scaled_obj3$scaled_nldr -->

<!-- scurve_nldr3 <- umap_scaled3 |> -->
<!--   ggplot(aes(x = emb1, -->
<!--              y = emb2))+ -->
<!--   geom_point(alpha=0.1, size=1, colour='#4daf4a') + -->
<!--   interior_annotation("c", c(0.08, 0.9)) -->

<!-- nldr_scaled_obj4 <- gen_scaled_data( -->
<!--   nldr_data = scurve_umap4) -->
<!-- umap_scaled4 <- nldr_scaled_obj4$scaled_nldr -->

<!-- scurve_nldr4 <- umap_scaled4 |> -->
<!--   ggplot(aes(x = emb1, -->
<!--              y = emb2))+ -->
<!--   geom_point(alpha=0.1, size=1, colour='#a65628') + -->
<!--   interior_annotation("d") -->

<!-- nldr_scaled_obj5 <- gen_scaled_data( -->
<!--   nldr_data = scurve_umap5) -->
<!-- umap_scaled5 <- nldr_scaled_obj5$scaled_nldr -->

<!-- scurve_nldr5 <- umap_scaled5 |> -->
<!--   ggplot(aes(x = emb1, -->
<!--              y = emb2))+ -->
<!--   geom_point(alpha=0.1, size=1, colour='#636363') + -->
<!--   interior_annotation("e") -->

<!-- nldr_scaled_obj6 <- gen_scaled_data( -->
<!--   nldr_data = scurve_umap6) -->
<!-- umap_scaled6 <- nldr_scaled_obj6$scaled_nldr -->

<!-- scurve_nldr6 <- umap_scaled6 |> -->
<!--   ggplot(aes(x = emb1, -->
<!--              y = emb2))+ -->
<!--   geom_point(alpha=0.1, size=1, colour='#984ea3') + -->
<!--   interior_annotation("f") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- scurve_error <- dplyr::bind_rows(scurve_umap_mse, -->
<!--                                  scurve_umap_mse2, -->
<!--                                  scurve_umap_mse3, -->
<!--                                  scurve_umap_mse4, -->
<!--                                  scurve_umap_mse5, -->
<!--                                  scurve_umap_mse6) -->

<!-- scurve_error <- scurve_error |> -->
<!--   mutate(a1 = round(a1, 2)) |> -->
<!--   filter(b1 >= 5) |> -->
<!--   group_by(method, a1) |> -->
<!--   filter(MSE == min(MSE)) |> -->
<!--   ungroup() -->

<!-- error_plot <- ggplot(scurve_error, -->
<!--          aes(x = a1, -->
<!--              y = sqrt(MSE), -->
<!--              color = method)) + -->
<!--     geom_point(size = 0.8) + -->
<!--     geom_line(linewidth = 0.3) + -->
<!--   scale_x_continuous(breaks = -->
<!--     sort(unique(scurve_error$a1))[ -->
<!--       seq(1, length( -->
<!--         unique(scurve_error$a1)),  -->
<!--         by = 5)]) + -->
<!--   scale_color_manual( -->
<!--     values=c('#e41a1c','#ff7f00','#4daf4a',  -->
<!--              "#a65628",'#636363', '#984ea3'))+ -->
<!--     ylab("RMSE") + -->
<!--     xlab(expression(paste("binwidth (", a[1], ")"))) + -->
<!--     theme_minimal() + -->
<!--     theme(panel.border = element_rect(fill = 'transparent'), -->
<!--           plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5), -->
<!--           axis.ticks.x = element_line(), -->
<!--           axis.ticks.y = element_line(), -->
<!--           legend.position = "none", -->
<!--           axis.text.x = element_text(size = 7), -->
<!--           axis.text.y = element_text(size = 7), -->
<!--           axis.title.x = element_text(size = 7), -->
<!--           axis.title.y = element_text(size = 7), -->
<!--           aspect.ratio = 1.5) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- free(error_plot) + wrap_plots( -->
<!--   scurve_nldr1, scurve_nldr2,  -->
<!--   scurve_nldr3, scurve_nldr4, -->
<!--   scurve_nldr5, scurve_nldr6,  -->
<!--   ncol = 2) -->
<!-- ``` -->

>>>>

```{r setup, include=FALSE}
options(repos = "https://cloud.r-project.org") ## set up CRAN mirror
knitr::opts_chunk$set(
  echo = FALSE, 
  cache=FALSE, 
  message=FALSE, 
  warning=FALSE,
  comment = ">",
  out.width = "100%",
  htmlwidgets.sizing = TRUE)

@@
